%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.3, 10 May 2020) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicon fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}


% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{DarkTeal}{HTML}{01626e}
\definecolor{DarkGreen}{HTML}{013220}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}

\definecolor{GoogleBlue}{HTML}{4285F4}
\definecolor{GoogleRed}{HTML}{DB4437}
\definecolor{GoogleYellow}{HTML}{F4B400}
\definecolor{GoogleGreen}{HTML}{0F9D58}

% \colorlet{name}{black}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
% \addbibresource{sample.bib}

\begin{document}
\name{Sreejith Kesavan}
\tagline{Staff Engineer | Nutanix, Inc. | Cloud Mobility, Virtualization, Distributed Systems}
% \photoR{2.5cm}{semk_bw}
\personalinfo{%
	% Not all of these are required!
	% You can add your own with \printinfo{symbol}{detail}
	\email{sreejithemk@gmail.com}
	\phone{(+91)-99-8684-9928}
	% \mailaddress{Nutanix, Inc., Bangalore}
	% \location{Bangalore, KA, IN}
	\homepage{foobarnbaz.com}
	\github{semk}
	\linkedin{sreejithemk}
}

\makecvheader

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}
	
	\cvsection{Experience}
	
	\cvevent{Staff Engineer}{Nutanix, Inc.}{Aug 2015 -- Present}{Bangalore, IN}
	\begin{itemize}
		\item Leading the development of a multi-cloud VM migration platform. \\Around 160k VMs migrated.
		\item Designed an agentless migration methodology for migrating Azure\\ virtual machines to on-premise AHV clusters.
		\item Improved the migration performance upto 7x for high latency, lossy\\ networks by leveraging KCP, a UDP based reliable protocol.
		\item Designed an application life cycle management system with upgrade\\ and rollback capabilities. 4.3k upgrades performed.
		\item Built a minimal Docker container host operating system based on\\ Alpine Linux to ship non-core products as a virtual appliance.
		\item Designed and developed core functionalities of a database migration\\ platform which comprises of designer, deployer and migrator modules.
		\item Developed a task execution framework in Python with support for\\  pause, resume, cancel operations and progress monitoring.
		\item Lead the design and development of a cluster health diagnostics tool.
	\end{itemize}
	
	\divider
	
	\cvevent{Member of Technical Staff}{NetApp, Inc.}{Sep 2012 -- Aug 2015}{Bangalore, IN}
	\begin{itemize}
		\item Developed data collection and reporting modules for the 7-Mode to Clustered Data ONTAP Transition Tool.
		\item Developed an XSLT based viewer for the inventory data collected by\\ the Inventory Collect Tool.
		\item Reduced the overall memory footprint of the collector module upto 3x and improved performance upto 2x.
		\item Developed a migration planner using PyQt to generate homogeneous and heterogeneous SAN migration plans which can be automated.
		\item Built a PyQt based GUI for viewing and uploading data collector bundle to a centralized NetApp filer.
	\end{itemize}
	
	\divider
	
	\cvevent{Development Engineer}{K7 Computing Pvt. Ltd.}{Feb 2009 -- Aug 2012}{Chennai, IN}
	
	\begin{itemize}
		\item Developed core services, Google App Engine compatible APIs and\\ Python SDK for a PaaS platform.
		\item Developed a FUSE file system for malware analysis, backed by NFS.
		\item Developed various modules of a virtualization management platform that supports Xen, OpenVZ and KVM hypervisors.
		\item Developed HyperVM API emulator for the virtualization management platform to work with WHMCS plugins.
		\item Developed a management console for data center administrators to manage virtual machines remotely.
		\item Contributed to Hypertable and Riak Python client library development.
	\end{itemize}
	
	\newpage
	
	\switchcolumn
	
	\cvsection{Education}
	
	\cvevent{B.Tech. in Computer Science and \\Engineering}{University of Calicut, KL, IN}{July 2004 -- June 2008}{}
	
	% \divider
	
	% \cvevent{HSE in Computer Science}{KPM Higher Secondary, KL, IN}{June 2002 -- May 2004}{}
	
	\cvsection{Honours}
	
	\cvachievement{\faMedal}{Engineering SuperHero, 2016}{The highest engineering accolade at Nutanix}
	
	\divider
	
	\cvachievement{\faTrophy}{Nutanix Hackathon 3.0, 2016}{Nutanix HCI orchestrator using TOSCA, \#1 in Top Ten Projects}
	
	\cvsection{Publications}
	
	\cvachievement{\faBook}{Linux For You, Oct 2009}{"The New Scheduler on the Block, Dedicated to Desktops" -- An article on BFS scheduler for Linux}
	
	\cvsection{Expertise}
	
	\cvtag{Microservices Architecture}
	\cvtag{API Design}\\
	\cvtag{Relational \& NoSQL DBs}
	\cvtag{Containers}
	\cvtag{Distributed Systems}
	\cvtag{Cloud Platforms}
	\cvtag{Virtualization}
	\cvtag{Service Mesh}
	\cvtag{RPCs}
	
	% \divider\smallskip
	
	% \cvtag{Docker}
	% \cvtag{Hypertable}
	% \cvtag{Riak}
	% \cvtag{AWS}
	% \cvtag{Azure}
	% \cvtag{App Engine}
	% \cvtag{SaltStack}
	
	\cvsection{Opensource}
	\begin{itemize}
		\item \href{https://github.com/cyclozzo/cyclozzo}{Cyclozzo}: PaaS cloud builder and manager
		\item \href{https://code.google.com/archive/p/enlargeweb}{EnlargeWeb}: VM deployer and manager
		\item \href{https://github.com/semk/voldemort}{Voldemort}: Static site generator for GH pages
		\item \href{https://github.com/semk/Pytt}{Pytt}: BitTorrent Tracker using Tornado
		\item \href{https://github.com/semk/RegexMate}{RegexMate}: Regular Expression Toolkit
		\item \href{https://github.com/semk/GameOfLife}{GameOfLife}: Game of Life simulation in PyQt
		\item \href{https://github.com/semk/GitFS}{GitFS}: FUSE filesystem that stores data on Git
		% \item \href{https://github.com/semk/Org2OPML}{Org2OPML}: ORG to OPML file converter
		% \item \href{https://github.com/semk/appy}{Appy}: Boilerplate for Python applications
	\end{itemize}
	
	\cvsection{Programming}
	\cvskill{Python}{5}
	% \divider
	\cvskill{Go}{5}
	% \divider
	\cvskill{C}{4}
	\cvskill{Erlang}{3}
	
\end{paracol}
\end{document}
