\documentclass[a4paper,12pt]{article}

\include{cv-commands}

\begin{document}

\setmainfont

\header
{Sreejith K}
{Development Engineer}
{Age: 25 years old\\
Email: sreejithemk@gmail.com\\
Tel: \smcp{(+91) 9940382162}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Formation}
\resumeitem{2004–2008}{B-Tech in Computer Science \& Engineering from Jyothi Engineering College, University of Calicut, Kerala.} \\

\resumeitem{2002-2004}{Higher Secondary Education in Computer Science from KPMHSS, Poothotta, Kerala.} 
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Technical Skills}

\resumeitem{Specialities}{Distributed Programming with Python and Erlang, NoSQL Databases, Virtualization, Infrastructure as a Service, Platform as a Service, Userspace Filesystems.}
\largeskip

\resumeitem{Programming Languages}{Python, Objective C, C, Erlang.}
\largeskip

\resumeitem{Databases}{MySQL, SQLite, Hypertable, MongoDB, Riak, Redis, Cassandra.}
\largeskip

\resumeitem{Recent Interests}{NoSQL Databases, Cocoa framework for Mac OSX \& iOS, Distributed and Parallel Programming with Erlang, Amazon Dynamo Architecture.}

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Professional Experience}

\resumeitem{Since Feb 2009}{Development Engineer at K7 Computing Private Limited.}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Projects}

\resumeitem{Cyclozzo,\\ Platform as a Service}{Cyclozzo is a meta cloud platform designed to support the latest PaaS APIs with minimal effort. Cyclozzo currently implements two of the most popular PaaS APIs: Google App Engine Python and Google App Engine Java. Cyclozzo continuously monitors application requests and makes sure that user applications are responsive at all times, while utilizing optimal server resources. When load goes up, Cyclozzo increases the number of application instances and also decreases them when requests come down. Cyclozzo does auto scale-out and scale-in while taking in to account the application's budget/plan.}
\largeskip

\resumeitem{EggPlug,\\ NAS and Cloud Storage}{EggPlug (www.eggplug.com) is a physical device which lets you access your digital media across the Internet. Contents across various other Physical plugs and desktop installations are kept in sync. User selected files/folders are backed incrementally onto Amazon S3. Devices are authenticated using OAuth protocol. One could simply consider this product as a NAS and Dropbox solutions combined.}
\largeskip

\resumeitem{FluidVM,\\ Hypervisor Manager}{FluidVM is a virtualization platform. One of the earliest products in is domain. It is a multi-hypervisor manager. FluidVM provides a unified interface to manage all open source hypervisors. A pure python implementation for which we developed our own development framework and billing solution. It comes integrated with third party billing solutions like WHMCS as well. All basic functionalities like backup, templatization, migration, SAN and Local storage management work seamlessly across all hypervisors. FluidVM provides fine grained user control and allows various levels of user configurations at runtime. FluidVM has an optional VLAN and bonding functionality along with Basic Firewall and traffic controlling.}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Personal Projects}

\resumeitem{Cyclozzo OSE}{Opensource Edition of the Cyclozzo Platform as a Service.}
\largeskip

\resumeitem{Voldemort}{Voldemort is a blog-aware static site generator using Jinja2 and Markdown templates. Inspired by Jekyll static site generator written in Ruby.}
\largeskip

\resumeitem{Appy}{A simple Application Framework for Python which simplifies the handling of commandline options, threading, multiprocessing and logging in Python.}
\largeskip

\resumeitem{HyperGAE}{A project that helps Google App Engine SDK to run on top of Hypertable.}
\largeskip

\resumeitem{GitFS}{A FUSE filesystem written in Python that stores data on Git(Hub).}
\largeskip

\resumeitem{PlayAsia API}{The Play-Asia.com API is a set of functions that allow you to retrieve data programatically using Python.}
\largeskip

\resumeitem{Riak Python Client}{Various fixes and feature additions to the Riak Python Client.}
\largeskip

\resumeitem{Riak Multi Index}{Multiple secondary index query support for Riak using Python.}
\largeskip

\resumeitem{Hypertable Python Client}{Various fixes and feature additions to the Hypertable Python Client using Boost Library.}
\largeskip

\resumeitem{Hypertable Deployment Script}{Automated deployment of Hypertable using Fabric.}
\largeskip

\resumeitem{Pytt}{Pytt is a BitTorrent Tracker written in Python using Tornado.}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Online Profiles}

\resumeitem{Personal Website}{http://foobarnbaz.com}
\shortskip

\resumeitem{GitHub}{https://github.com/semk}
\shortskip

\resumeitem{LinkedIn}{http://in.linkedin.com/pub/sreejith-k/15/50b/69}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{interestsblock}{Interests \& Activities}
	\interest{idea}{Learning new technologies} &
	\interest{gnu}{Free Software Movement}\\
	&\\
	\interest{hack}{Solving problems} &
	\interest{bike}{Cycling!} 
\end{interestsblock}

\end{document}
